\textbf{{\Large {Recursive algorithms, branching coefficients and applications}}}

### 2010-07-01 AffineLieAlgebras/InformalNotes/article.tex
PDF regen

Consider the embedding $\mathfrak{a}\subset \mathfrak{g}$ where
$\mathfrak{a}=\hat A_1\oplus \hat A_1$ and $\mathfrak{g}= \hat A_3$,
which is the affine extension of the special embedding $A_1\oplus A_1\subset A_3$.
To construct this injection we use the method presented in \cite{vasilevich1986method}.
We start with the 4-dimensional module $L_{A_1\oplus A_1}^{(1,1)}$.
Its diagram $\mathcal{N}_{A_1\oplus A_1}^{(1,1)}
= \left\{\nu_1=(1,1),\; \nu_2=(-1,1),\; \nu_3=(1,-1),\; \nu_4=(-1,-1)\right\}$
is presented in Figure \ref{fig:A_1+A_1_to_A3}.

>>>>

Consider the embedding $\mathfrak{a}\subset \mathfrak{g}$ where
$\mathfrak{a}=\hat A_1\oplus \hat A_1$ and $\mathfrak{g}= \hat A_3$,
which is the affine extension of the special embedding $A_1\oplus A_1\subset A_3$.
To construct this injection we use the method presented in \cite{vasilevich1986method}.
We start with the 4-dimensional module $L_{A_1\oplus A_1}^{(1,1)}$. Its diagram
$$\mathcal{N}_{A_1\oplus A_1}^{(1,1)}= \left\{\nu_1=(1,1),\; \nu_2=(-1,1),\; \nu_3=(1,-1),\; \nu_4=(-1,-1)\right\}$$
is presented in Figure \ref{fig:A_1+A_1_to_A3}.
